### 2023-08-25 main.tex
Fix 2

	\com{Double check this. Sum looks strange}
and where
 \begin{equation}\label{CiEquation}
	c_{y}=\begin{cases}
		1\quad \text{if}\quad \tau_{y}\neq 1\\
		0\quad \text{if}\quad \tau_{y}=1
	\end{cases}\qquad \forall y\in \{1,\ldots,L\}

@@

%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},1})}
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
\subsubsection{The steady state of $H$}\label{subsectionSSH}
The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
    |\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
 \Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},1}\right) 
\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
\sum_{c_{1}=0}^{1-\delta_{\eta_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},1})}
where we have introduced, $\forall x\in \{1,\ldots,L\}$
	\eta_{x}(b)=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
		d_{x}\qquad &\text{otherwise}
	\end{cases}%\qquad \theta_{x}=\begin{cases}
		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
	%	1 \qquad &\text{otherwise}
	%\end{cases}
The dependence of $\eta_{x}(b)$ with respect to $b$ is usually understood for the sake of notation. 
\begin{equation}\label{steadyStateH-coeff}
        \Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
        \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},1}\right) 
        \sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},1}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
  \prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
 \\ &
 \beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $\tau_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
\begin{equation}\label{LinkABS-corr}
\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.

@@

\section{Non-integrable chain}

>>>>

	%\com{Double check this. Sum looks strange}
%and where
% \begin{equation}\label{CiEquation}
%	c_{y}=\begin{cases}
%		1\quad \text{if}\quad \tau_{y}\neq 1\\
%		0\quad \text{if}\quad \tau_{y}=1
%	\end{cases}\qquad \forall y\in \{1,\ldots,L\}

@@

%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},1})}
	\end{split}
\end{equation} 
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
\begin{flushright}
    $\square$
\end{flushright}

@@

\section{Mapping to equilibrium}
\subsection{The non local transformation}\label{SectionNonLocalTrasformation}
This matrix is 
%We have that 
%	\left[H_{0},Q^{0}_{2L}\right]=0\qquad \left[H^{''},Q_{2L}\right]=0
%thus it is enough to look for a matrix $W$ such that 
%\begin{equation}\label{GoalWQ}
%	Q^{2L}W=WQ_{2L}^{0}
Formula \eqref{W-extended} comes from standard perturbation theory. However, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system. This expression, as it will be show in the following sections, allows to find explicit expression of the eigenvector by the Bethe ansatz and also allows to retrieve again the steady state of $H^{''}$ by applying $W$ to the ground state. To find it, we use the Quantum Inverse Scattering Method (QISM). We first present the simpler case of $gl(2)$, then we try to adapt the proof the general $gl(N)$. 
We can apply the \textit{quantum inverse scattering method} to this process. We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We introduce the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$
and the $K$-matrices
We define the \textit{transfer matrix}
where we used the double row monodromy defined as

\end{itemize}
where
\begin{align}
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\end{align}
\subsection{Charges}
Then we have
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
			-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
			0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
			\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
			0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
			0&0&0&\ldots&0&1+x
		\end{pmatrix}\right.
		\\& \left.
		\;\;\;\begin{pmatrix}
			D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
			D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
			\vdots&\vdots&\ddots&\vdots&\vdots\\
			D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
			B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
		\end{pmatrix}\right)
	\end{split}
\end{equation}
Therefore we can write the polynomial expansion
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=&
		(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
	\end{split}
\end{equation}
We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
We can also introduce 
\begin{equation}
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
\end{equation}For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
\begin{equation}
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
\end{equation}
In the following it will be clear that only the first three coefficients of the diagonal elements and only the first coefficient of the non diagonal element are needed. 
\begin{itemize}
	\item For the element $D_{N,N}(x)$: 
%The coefficients that we need are the following:
%\begin{equation}
%	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
where 
\begin{equation}
	D_{N,N}^{2L+1}=I^{tot}
\end{equation}
\begin{equation}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
\end{equation}
\begin{equation}
	D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
\end{equation}
%\begin{equation}
%	\begin{split}
	%	D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}
%	\end{split}
%\end{equation}
\begin{comment}
{\color{blue}ok}

We observe that $\forall i,j=1,\ldots,N-1$
\begin{equation}
	\sum_{a\neq b}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
\end{equation}
then 
\begin{equation}
	D_{N,N}^{2L-1}=e_{NN}^{tot}\left(2e_{NN}^{tot}+I^{tot}\right)-\sum_{j=1}^{N}e_{jj}^{tot}%=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
\end{equation}
Then

{\color{blue}ok?}where we used $
\sum_{i=1}^Ne_{ii}^{tot}=L$. 
\end{comment}
\item For $D_{i,i}(x)$ with arbitrary $ i\in\{1,\ldots,N-1\}$ 
%\begin{equation}
%	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}
	D_{ii}^{2L-1}=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}
\end{equation}
%\begin{equation}\label{a2lm1}
%	\begin{split}
	%	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=1\,:\,j\neq i}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
	%	&=e_{11}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
	%	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
%		&=e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
%	\end{split}
%\end{equation}

%We rewrite
%\begin{equation}
%	\begin{split}
	%	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=1}^{N%-1}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
%	\end{split}
%\end{equation}
%then
%\begin{equation}
%	\begin{split}
%		D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}%=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
%	\end{split}
%\end{equation}

%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
%\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
\item For $B_{j}(x)$  $\forall j=2,\ldots,L$ 
\begin{equation}
		B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{equation}
\begin{comment}
\begin{equation}
B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
B_{j}^{2L-1}=2e_{j1}^{tot}+
2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
B_{j}^{2L-1}&=
2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
%	&=
%	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{split}
\end{equation}
Thus
\begin{equation}
\boxed{	B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}}
\end{equation}
\end{comment}
\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

\begin{align}
Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N\\
Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1\\
Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is 
%\begin{equation}
%\begin{split}
%Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
%\end{split}
%\end{equation}
\begin{equation}\label{Q0Exp}
\begin{split}
Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}
%\begin{equation}	
%\begin{split}
%Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%\end{split}
%\end{equation} 
We also introduce 
\begin{equation}
\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{equation}
therefore we can write 
\begin{equation}
Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

Consider the matrix $Q_{0}^{2L}$ defined in \eqref{Q0Exp}. All terms are diagonal except the last one. However, this last non-diagonal term acts diagonally on the states. Indeed, can be identified with the second Casimir of the $gl(N-1)$ subalgebra. We denote it by $\hat{C}_{2}$ and it reads
\hat C_2^{N-1}= \sum_{i,j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}
We denote its eigenvector by $C_{2}^{N-1}$. On the Bethe states (and on the irrep decomposition of the spin chain) it acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e. 
C_2^{N-1}=\sum_{j=1}^{N-1}\ell_j(\ell_j -N+2)+\frac{1}{6}(N-1)(N-2)(N-3)
 	\ell_{j}=\mu_{j}+N-j
with $\mu_{j}$ the representation labels of tensor product over the chain of the fundamental representation of $gl(N)$ (it can be decomposed by branching rule).  
Thus the eigenvalues of the transfer matrix can be writen as 
\Lambda(x)&= \Lambda_{2L+2} x^{2L+2}+ \Lambda_{2L+1} x^{2L+1}+ \Lambda_{2L}x^{2L}+\ldots
\\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_1+1)-(N+2)(L-m_1)+2C_{2}^{N-1}\right)x^{2L}+\ldots
Thus the difference is of order $2L$ and becomes
\Lambda(x)-T_0(x)=x^{2L}\left(\Lambda_{2L}-Q_{2L}^0\right)+\ldots
By taking the limit we obtain
\lim_{x\to\infty}\frac{2x+N}{\Lambda(x)-T_0(x)}B_{i}(x)=\frac{2}{\Lambda_{2L}-Q_{2L}^0}B_i^{2L-1}
\paragraph{Exchange relations between charges}
Using \eqref{EX1}, \eqref{EX2} and \eqref{EX3} we obtain for every $i,j\in\{1,\ldots,N-1\}$ 
\begin{equation}\label{ExQ0B-charges}
Q_{0}^{2L}B_{i}^{2L-1}=B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{j=1\,:\,j\neq i}^{N-1}B_{j}^{2L-1}D_{j,i}^{2L}
%In particular for the case $N=3$ we have
%	\begin{split}
%	Q_{0}^{2L}B_{1}^{2L-1}&=B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{3,3}^{2L})\right)-2B_{2}^{2L-1}D_{2,1}^{2L}
%	\\
%	Q_{0}^{2L}B_{2}^{2L-1}&=B_{2}^{2L-1}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{3,3}^{2L})\right)-2B_{1}^{2L-1}D_{1,2}^{2L}
%	\end{split}
Other useful exchange relations are 
\begin{equation}\label{ExDNB-charges}
D_{N,N}^{2L}B_{i}^{2L-1}&=B_{i}^{2L-1}\left(D_{N,N}^{2L}+D_{i,i}^{2L+1}-D_{N,N}^{2L+1}\right)%\\
%D_{33}^{2L}B_{2}^{2L}&=B_{2}^{2L}\left(D_{33}^{2L}+D_{22}^{2L+1}-D_{33}^{2L+1}\right)
\begin{equation}\label{ExDiB-charges}
D_{i,i}^{2L}B_{i}^{2L-1}&=B_{i}^{2L-1}\left(D_{i,i}^{2L}+D_{i,i}^{2L+1}-D_{N,N}^{2L+1}\right)%\\
%D_{22}^{2L}B_{2}^{2L}&=B_{2}^{2L}\left(D_{22}^{2L}+D_{22}^{2L+1}-D_{33}^{2L+1}\right)
and finally
\begin{equation}\label{ExDijB-charges}
D_{i,j}^{2L}B_{i}^{2L-1}&=B_{i}^{2L-1}D_{i,j}^{2L}+B_{j}^{2L-1}\left(D_{i,i}^{2L+1}-D_{N,N}^{2L+1}\right)%	D_{21}^{2L}B_{2}^{2L-1}&=B_{2}^{2L-1}D_{21}^{2L}+B_{2}^{2L-1}\left(D_{22}^{2L+1}-D_{33}^{2L+1}\right)
While, for $i,j\in\{1,\ldots,N-1\}$ such that $i\neq j$
\left[D_{j,j}^{2L},B_{i}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},B_{j}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},D_{j,i}^{2L}\right]=0%\qquad \left[D_{12}^{2L},B_{2}^{2L-1}\right]=0\qquad \left[D_{11}^{2L},B_{2}^{2L-1}\right]=0
{\color{blue}Using them we also have 
	&Q_{0}^{2L}B_{1}^{2L-1}Q_{0}^{2L}B_{2}^{2L-1}\\=&B_{1}^{2L-1}B_{2}^{2L-1}\left(Q_{0}^{2L}-2(D_{11}^{2L}+D_{22}^{2L}+2D_{33}^{2L})+4(D_{33}^{2L+1}-D_{11}^{2L+1})\right.\\-&\left.2B_{1}^{2L-1}B_{1}^{2L-1}D_{12}^{2L}-2B_{2}^{2L-1}B_{2}^{2L-1}D_{21}^{2L}\right)\left(Q_{0}^{2L}-2(D_{22}^{2L}+D_{33}^{2L})\right)
	\left(-2B_{1}^{2L-1}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{11}^{2L}+D_{33}^{2L})+4(D_{33}^{2L+1}-D_{11}^{2L+1})\right)+8B_{1}^{2L-1}B_{2}^{2L-1}D_{21}^{2L}\right)D_{12}^{2L}
\end{equation}}{\color{blue}Probably it is not useful}
\section{Conserved charges form of W}
By using the QISM results found in the previous section it is possible to rewrite $W$ in function of first non-trivial conserved charges of the system. This is possible because , thanks to integrability
	[H,T(x)]=0
and moreover $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$ with the property that, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can look for a matrix $W$ such that 
	Q^{2L}W=WQ_{0}^{2L}
Arguing as in section \ref{SectionNonLocalTrasformation}, we can show that 
\begin{equation}\label{WInCharges}
	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{m}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{m}+\epsilon-Q^{2L}_{0}-\mathcal{Q}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
Since $Q^{2L}$ and $H$ are isospectral the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones. The advantage is that now we can do more with this more with this expression. Hopefully, using exchange relation between charges, we could try to handle \eqref{WInCharges} and rewrite it independently from the equilibrium eigenvectors. Moreover, we can use it to extract the steady state by rising the vacum state. 
\subsection{The gl(2) case}
In this simpler situation the double row monodromy reads
	U_{0}=\begin{pmatrix}
		D_{1,1}(x)&C_{1}(x)\\
		B_{1}(x)&D_{2,2}(x)
Therefore, using the conserved charges and formula \eqref{WInCharges} we have
\begin{equation}\label{W}
	W=\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|
Power expanding the matrix $W$ with respect to $\Delta=(\alpha-\beta)$ and making it act on 
